Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated tables fixed
Updated tables and results done

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had lower hazard and slower speed of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95% CrI: 0.80, 0.96) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women. However, lower hazard and speed was observed to remain after age or multivariable adjustment only in daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models. In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared against men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were more than 97.5% sure that these posterior HRs were distributed below the null value. No apparent associations were observed between milk intake and hazard of cerebral infarction among women.

@@

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed from happening among Japanese male daily milk consumers compared with non-consumers.

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015], we further updated with more comprehensive and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event. A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999].
<!-- - potential biological reasons -->

@@

\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\

@@

\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\

>>>>

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models. In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared to men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs distributed below the null value was greater or equal to 97.5%. No evidence was found about the associations between milk intake and hazard of cerebral infarction mortality among women.

@@

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed among Japanese male daily milk consumers compared with non-consumers.

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015]. Moreover, we further updated with more comprehensive and more straightforward evidence about whether and how certain the evidence had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men. A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999]. 
<!-- - potential biological reasons -->

@@

\hspace{1em}Mean AF (SD) & 1 & 0.93 (0.24) & 1.23 (0.38) & 1.14 (0.33) & 1.04 (0.25)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.33) & (0.93, 1.98) & (0.87, 1.83) & (0.83, 1.55)\\
\hspace{1em}Mean HR (SD) & 1 & 0.89 (0.22) & 1.26 (0.26) & 1.15 (0.23) & 1.02 (0.19)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.39) & (0.90, 1.90) & (0.83, 1.74) & (0.78, 1.51)\\
\hspace{1em}Pr(HR < 1) & - & 73.2\% & 9.5\% & 24.8\% & 53.3\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 1.21 (0.32) & 1.16 (0.30) & 0.98 (0.19) & 0.97 (0.14)\\
\hspace{1em}95\% CrI & - & (0.95, 2.08) & (0.93, 1.95) & (0.79, 1.48) & (0.84, 1.43)\\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.37 (0.33) & 1.25 (0.28) & 0.94 (0.22) & 0.92 (0.17)\\
\hspace{1em}95\% CrI & - & (0.89, 2.18) & (0.87, 1.95) & (0.63, 1.52) & (0.69, 1.40)\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 8.5\% & 14.2\% & 70.1\% & 79.4\%\\

@@

\hspace{1em}Mean AF (SD) & 1 & 1.19 (0.19) & 1.12 (0.15) & 0.96 (0.12) & 0.97 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.94, 1.62) & (0.92, 1.49) & (0.78, 1.21) & (0.83, 1.18)\\
\hspace{1em}Mean HR (SD) & 1 & 1.38 (0.29) & 1.21 (0.22) & 0.91 (0.18) & 0.94 (0.14)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.89, 2.02) & (0.85, 1.70) & (0.62, 1.34) & (0.69, 1.25)\\
\hspace{1em}Pr(HR < 1) & - & 7.3\% & 15.6\% & 72.8\% & 70.0\%\\

### 2020-07-14 Paperfolder/Paperfolder.tex
updated tables fixed
Updated tables and results done

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had lower hazard and slower speed of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95\% CrI: 0.80, 0.96)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and more than 94.6\% in women. However,
lower hazard and speed was observed to remain after age or multivariable
adjustment only in daily male milk consumers. Specifically, the mean
(sd; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
male consumers of milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and
0.80 (sd = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
be smaller than the null value (=1). Daily female milk consumers had
posterior AFs and HRs that was distributed with means of 0.97 (sd =
0.09; 95\% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17)
which had 78.0\% of chance that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic
stroke were found to contain the null value for either men or women
among all fitted models. In contrast, men who had milk intake frequency
higher than 1-2 times/week were found to be associated with averagely
17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
cerebral infarction compared against men who never drank milk (Model 2
in \textbf{Table \ref{tab:tab2}}). We were more than 97.5\% sure that
these posterior HRs were distributed below the null value. No apparent
associations were observed between milk intake and hazard of cerebral
infarction among women.

@@

In the JACC study cohort, our analysis showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke mortality events were delayed from happening among Japanese male
daily milk consumers compared with non-consumers.

These findings are in line with our previous report
\citep{wang_milk_2015}, we further updated with more comprehensive and
more forthright evidence about whether and how certain we could hold
about daily consumption of milk is contributing to a postponed stroke
(mostly cerebral infarction) mortality event. A recent dose-response
meta-analysis of 18 prospective cohort studies had also shown a similar
negative association \citep{DeGoede2016} between milk consumption and
risk of stroke. The same meta-analysis however also found a slightly
higher risk of stroke per 200 g/day whole milk intake from five cohort
studies that were conducted on European or American population
\citep{goldbohm2011dairy, Iso1999}.

>>>>

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and greater than 94.6\% in women. However,
lower hazard and delayed time-to-event was observed to remain after age
or multivariable adjustment only among daily male milk consumers.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted AF and HR for daily male consumers of milk were
0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95\% CrI:
0.69, 0.93) with a probability of 99.0\% to be smaller than the null
value (=1). Daily female milk consumers had posterior AFs and HRs that
was distributed with means of 0.97 (sd = 0.09; 95\% CrI: 0.88, 1.10) and
0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of chance
that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic
stroke were found to contain the null value for either men or women
among all fitted models. In contrast, men who had milk intake frequency
higher than 1-2 times/week were found to be associated with averagely
17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
cerebral infarction compared to men who never drank milk (Model 2 in
\textbf{Table \ref{tab:tab2}}). Probability that the posterior HRs
distributed below the null value was greater or equal to 97.5\%. No
evidence was found about the associations between milk intake and hazard
of cerebral infarction mortality among women.

@@

In the JACC study cohort, our analysis showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke mortality events were delayed among Japanese male daily milk
consumers compared with non-consumers.

These findings are in line with our previous report
\citep{wang_milk_2015}. Moreover, we further updated with more
comprehensive and more straightforward evidence about whether and how
certain the evidence had shown about daily consumption of milk is
contributing to a postponed stroke (mostly cerebral infarction)
mortality event among Japanese male daily milk drinker. A recent
dose-response meta-analysis of 18 prospective cohort studies had also
shown a similar negative association \citep{DeGoede2016} between milk
consumption and risk of stroke. The same meta-analysis however also
found a slightly higher risk of stroke per 200 g/day whole milk intake
from five cohort studies that were conducted on European or American
population \citep{goldbohm2011dairy, Iso1999}.
